Dealing with Consumer Uncertainty: Online Product Reviews and What makes them helpful?

### 2022-09-29 Paper.Rmd
this is torture at this point

In order to decrease the uncertainty, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. However, since there are other ways to objectively evaluate a movie such as quality of its effects or its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

The rationality why the statistical results for search goods came out just as expected can be accredited to their objective features. Properties of electronics are easily evaluated prior purchase. This means that it is comparatively easier to collect information on search goods than experience goods. Other than online consumer reviews on an online retail website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals. Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on a camera. Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.

-   more elab is needed here

```{=html}
<!-- -->
```
-   you can discuss about the fluidity of search and exp attributes

A similar strong support for Negativity Bias can't be observed in the case of movies. Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating. According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough. This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients there so no matter the Review Length is U-Shaped function is observed. However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens. This means that potential buyers require more elaboration when a review is rated low. For experience goods, high rated reviews become more helpful on the average when reviews are short. This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021]. Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.

@@

Another reason may arise from the subjective nature of the experience attributes of the movies. Negative words, in the case of electronics, may have narrower range of meanings because what they try to convey directly relates the to quality of the good itself. The quality of the good is easily accessible because of the fact that electronics have dominant search attributes. Thus, negative words probably translates as potential monetary risks rather than affecting emotions. A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility. Furthermore, electronics are usually bought to be used for a comparatively long period of time. A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important. Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future. On the other hand, the monetary risks associated with a bad movie are relatively lower. Consumers can go to cinema, buy a DVD or access the movie as a part of their subscription plan on platforms such as Netflix. Subscription or ticket fees aren't the only cost for the consumer. In order to consume the product the consumer must spend the time that is equal to the duration of the movie. Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time. Additionally, laptops, phones and televisions could be considered as tools to consume products such as software and media whereas movies themselves can be considered as consumed after they were watched for the first time. Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device. Therefore, negative words in a movie review may not alert the consumer for potential monetary losses. Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.

@@

Firstly, as @mudambi2010 pointed out that potential selection bias exist in the data. It is not possible to know how many people actually read a particular review. Additionally, there is a strong possibility that as a review gets more votes this is going to draw more attention to the particular review. This can cause a positive feedback loop and this feedback loop can increase the chances that an observation making into the sample which leads to a selection bias. To fight with this, researchers usually resorted to setting a threshold of total votes where reviews with small amount of votes were filtered out of the sample. Furthermore, a multi-level regression model was developed by @kuan2015 in order to overcome the selection bias. In the first level of the regression the researchers modeled the binary case of wheter a review gets voted or not. After what makes a review voted was established, they progressed to the next stage of modelling the review helpfulness. Along with the multi-level model results they also shared OLS results where non-voted reviews were filtered from the data. Most of the significance and coefficient signs weren't different but coefficients differed in magnitude.

Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature. Let alone different methodologies, even the utilizations of similar variables were contrasting. For instance, review extremity was employed in three different ways by researchers. This paper and some others use review ratings as it is. Another group of studies took the differences of review ratings from the mean rating of a given product. This is usually called Review Inconsistency. The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5). In some studies these dummy variables were extended to negative and positive extreme dummies as well. The differences isn't limited to Review Rating. The usages the dependent variable, Perceived Helpfulness, diverged as well. In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression. Furthermore, some studies converted the percentage of the helpfulness into a binary problem where over 50% helpfulness score was considered as a helpful review. As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well. All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.

-   talk about the limitations as we go, selection bias and omitted variables, different utilizations of variables,

-   talk about whatever we speculate we are omitting the readers buying motivation, their trust towards strangers, search/exp classification is too simple,

>>>>

In order to decrease the uncertainty, search costs must be reduced. In Section \@ref(search-and-experience-goods-classification) it was mentioned that the action of search was costlier for Experience Goods than Search Goods. Furthermore, people tend to have homogeneous opinions about Search Goods [@hong2014]. This might mean that information cues are much more uniform for Search Goods. [@huang2015; @baek2012]. In other words, there are limited ways to construct a review because search attributes are more objective. Therefore, there might be a positive linear relationship between Perceived Helpfulness and Review Length because longer reviews can help the consumers in their decision making process by increasing the amount of information they have. However, since the attributes of electronics are objectively identifiable and limited (storage space of a phone, RAM of a laptop, color depth of a TV etc.) there aren't much to review for a reviewer. Because of this, there might be diminishing marginal returns to Review Length [@schindler2012; @huang2015]. On the contrary, for Experience Goods, people have tendency to form heterogeneous opinions [@hong2014]. This means that movie reviews are much more subjective by nature. Since there are less objectivity, a helpful review to one person might not be helpful to another. However, since there are other ways to objectively evaluate a movie such as quality of its effects or its budget and how well this budget is utilized, a weaker positive linear relationship is expected. Therefore it is hypothesized that:

@@

The rationality why the statistical results for search goods came out just as expected can be accredited to their objective features. Properties of electronics are easily evaluated prior purchase. This means that it is comparatively easier to collect information on search goods than experience goods. Other than online consumer reviews on a retailer's website, a potential buyer has an arsenal of product reviews which are available on tech enthusiastic websites where electronics are reviewed by professionals. Furthermore, some channels on YouTube offer product reviews where the reviewer inspects the product in question on a camera. Thus, the potential buyer can gather a great amount of information even before accessing to the online retailer's website.

-   more elab is needed here
-   you can discuss about the fluidity of search and exp attributes

A similar strong support for Negativity Bias can't be observed in the case of movies. Only evidence for Negativity Bias was the significant linear interaction term between Review Length and Review Rating. According to this result the U-Shaped function of Review Rating is only observable when Review Length is high enough. This is actually the case for search goods as well but the interaction term doesn't interfere with the sign of the other coefficients so no matter the Review Length is U-Shaped function is observed. However, this is certain that as the review rating gets higher the review loses its diagnostic value for both for experience and search goods because the coefficient of the Review Length weakens. This means that potential buyers require more elaboration when a review is rated low. For experience goods, high rated reviews become more helpful on the average when reviews are short. This also might be a sign for positivity bias where people pay more attention to reviews which were aligned with their own feelings [@zhu2021]. Since experience attributes are naturally subjective it is logical to think that readers look for reviews that they agree.

@@

Another reason may arise from the subjective nature of the experience attributes of the movies. Negative words, in the case of electronics, may have narrower range of meanings because what they usually try to convey directly relates the to quality of the good itself. The quality of the good is easily accessible because of the fact that electronics have dominant search attributes. Thus, negative words probably translates as potential monetary risks rather than affecting emotions. A risk might be exemplified as purchasing a sub-par performing laptop with a given budget, in other words getting sub-optimal utility. Furthermore, electronics are usually bought to be used for a comparatively long period of time. A smartphone or a television can serve its owner for years so negative cues which relate to below average durability are very important. Buying a sub-durable product for a given budget can only increase the chances that the consumer will have to buy the same type of product prematurely in the future. On the other hand, the monetary risks associated with a bad movie are relatively lower. Consumers can go to cinema, buy a DVD or access the movie as a part of their subscription plan on platforms such as Netflix. Subscription or ticket fees aren't the only cost for the consumer. In order to consume the product the consumer must spend the time that is equal to the duration of the movie. Of course, the consumer can stop watching the movie anytime if it is too unbearable for her so she doesn't waste any more time. Because of these reasons the money spent on a movie might be irrelevant to an average consumer since accessing a movie is relatively cheaper than owning an electronic device. Therefore, negative words in a movie review may not alert the consumer for potential monetary losses. Instead, negative words could render a review in question unpleasant because emotions are priority in the case of consumption of movies.

@@

Firstly, as @mudambi2010 pointed out that potential selection bias exist in the data. It is not possible to know how many people actually read a particular review. Additionally, there is a strong possibility that as a review gets more votes this is going to draw more attention to the particular review. This can cause a positive feedback loop and this feedback loop can increase the chances that an observation making into the sample which leads to a selection bias. To fight with this, researchers usually resorted to setting a threshold of total votes where reviews with small amount of votes were filtered out of the sample. Furthermore, a multi-level regression model was developed by @kuan2015 in order to overcome the selection bias. In the first level of the regression the researchers modeled the binary case of whether a review gets voted or not. After what makes a review voted was established, they progressed to the next stage of modelling the review helpfulness. Along with the multi-level model results they also shared OLS results where non-voted reviews were filtered from the data. Most of the significance and coefficient signs weren't different but coefficients differed in magnitude.

Secondly, as pointed out in Section \@ref(literature-review), there were many different research designs present in the literature. Let alone different methodologies, even the utilizations of similar variables were contrasting. For instance, review extremity was employed in three different ways by researchers. This paper and some others use review ratings as it is. Another group of studies took the differences of review ratings from the mean rating of a given product. The resulting variable is usually called Review Inconsistency. The last group of researchers utilized a dummy variable for neutral reviews (3 out of 5) and extreme reviews (1,2,4,5 out of 5). In some studies these dummy variables were extended to negative and positive extreme dummies as well. The differences isn't limited to Review Rating. The usages the dependent variable, Perceived Helpfulness, diverged as well. In some circumstances only absolute Helpful votes were used along with Negative Binomial Regression. Furthermore, some studies converted the percentage of the helpfulness into a binary problem where reviews with over 50% helpfulness score was considered as a helpful review. As a last example to different applications, scale transformations (logarithmic transformation, etc.) were applied liberally as well. All in all, it is clear that there is no standard approach in the literature which might be the reason why there are many conflicting results.

Potential omitted variables such as consumer's buying motivation or their trust towards strangers may also explain the conflicting or unexpected results as pointed out by @zhu2021. A person who is more agreeable high likely will find many more reviews helpful on the average. Additionally, buying motivation might play an important role in explaining the review helpfulness. Above, it was speculated that some consumers might have tendency towards certain brands or products. Favored brands might not be the only factor that affects the consumer motivation. For instance, a consumer with limited amount of budget may find positive reviews of products that have suitable prices helpful. Thus the product price relative to the consumer's budget can also be used as an indicator.

-   talk about review and reviewer related determinant, search/exp classification is too simple,
